The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
intro edits

# Introduction
Our inference regarding the ecological processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability
[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
Meanwhile, in the context of animal behaviour, certain behaviours are scale
dependent, for example, acoustic communication in birds occurs over variable
spatial scales [@Luther_2009]. We posit that animal behaviour and, more
specifically, the social environment that animals experience must also be
scale-dependent.

@@

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in the social, spatial, and
temporal scale improve predictions associated with biological differences in
seasonal resource availability and social association? We conclude with
perspectives for further development and application of scale in multilayer
networks with respect to phenotypes and individual fitness [@Webber_2018],
movement ecology and collective movement [@Jolles_2019], and habitat selection
and space use. <!-- TODO: (REF)--> <!-- TODO: Webber reference should be 2018,
but defaulting to 2017-->

>>>>

# Introduction
Our inference regarding the ecological processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability
[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989], among others.
Meanwhile, in the context of animal behaviour, certain behaviours are scale-dependent; for example, acoustic communication in birds varies with spatial scales [@Luther_2009]. We posit that it is important to consider that animal behavior within the social environment will be scale-dependent.

@@

Our examinations is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in the social, spatial, and
temporal scale improve predictions associated with biological differences in
seasonal resource availability and social association? We conclude with
perspectives for further development and application of scale in multilayer
networks with respect to phenotypes and individual fitness [@Webber_2018],
movement ecology and collective movement [@Jolles_2019], and habitat selection
and space use<!-- TODO: (REF)--> . 
<!-- TODO: we answer the first question in the discussion, but not the second-->
<!-- TODO: Webber reference should be 2018, but defaulting to 2017-->
